---
title: "class_Oct10.Rmd"
author: "Vinay K L"
date: "2023-10-10"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Regular Expressions continued

## Sequences

\\d - match a digit character - like 0,1,2,3,4
\\D - opposite of digit charcter - non-digits
\\s - match a space character
\\S - match a non-space character

```{r}
sub("\\d", "_", "Covid 19")
```
```{r}
gsub("\\D", "_", "Covid 19")
```
```{r}
sub("\\s", "_", "Covid 19")
```
```{r}
sub("\\S", "_", "Covid 19")
```


# Character class

[^aeiou] - match anything other than lowercase vowel

```{r}
d <- c("car", "bike", "plane", "boat", "oct 07", "I-II-III")

#looking for 'e' or 'i'

grep(pattern = "[ei]", x = d, value = TRUE)
```
```{r}
grep(pattern = "[01]", x = d, value = TRUE)
```

# POSIX Character Classes

[[:lower:]] - lower case letters
[[:alpha:]] - alphabetic characters
[[:digit:]] - Digits
[[:alnum:]] - alphanumeric characters
[[:punct:]] - puntuation characters

```{r}
gsub(pattern = "[[:blank:]]", replacement = "", x = d )
```
```{r}
gsub(pattern = "[[:lower:]]", replacement = "_", x = d)
```

# Quantifiers

Number of times regex needs to run instead of 1 or all

? - zero or at most once
* - zero or more times
+ - one more more times
{n} - exactly n times
{n,} - n or more times
{n,m} - at least n times but not more than m times. 

```{r}
sts <- row.names(USArrests)

sts
```

```{r}
grep(pattern = "n?", x = sts, value = TRUE)
```

```{r}
grep(pattern = "n{2}", sts, value = TRUE)
```

# position of the pattern within a string

^ - match start of the string
$ - end of the string
```{r}
# \b - matches the empty string at either edge of a word. 
## \B matches the empty string provided it is not at a naedge of a word
```


```{r}
strings <- c("abcd", "cdab", "cabd", "c abd")
grep("ab", strings, value = TRUE)
```

```{r}
grep( "^ab", strings, value = TRUE )
```

```{r}
grep("ab$", strings, value = TRUE)
```
```{r}
grep("\\bab", strings, value = TRUE)
```

```{r}
grep("\\Bab", strings, value = TRUE)
grep("ab\\B", strings, value = TRUE)
```


# Operators 
. matches any single character
[...] - matches any one of the characters inside the bracket
[^...] - matches any other char except those inside the brackets


# Web scrapping


